### 2024-06-26 conteudo/introduction/intro.tex
Add initial reformuled version of the introduction

This research is divided into two phases. On the first phase, we will propose, build and validate a tool capable to indentify code 
duplications in function level for the C programming language, we expects this proposed tool to indentify code duplications
in the Linux kernel, as in our preliminary investigation the code files in the kernel is commonly a union of duplicated and 
nonduplicated functions. To validate the tool, we will do a triangulation of results by evaluate our tool in the code duplication
databases used in the formal literature and (DO NOT KNOW IF I REALLY WILL DO THIS) doing a empirical analyses in a set
of randomly selected codes of the AMD Display driver which our proposed tool claims that is a duplications. 
The detailed explication of how we will validate our tool is demonstrated in the Chapter \ref{cha:method}.

Given the first phase completion, we have a validated tool to indentify code duplications in the Linux kernel 
context and we can move on to how mitigate this duplications, which compreend the second phase of our research.

(I DO NOT HAVE MORE A PLACE TO FIT THIS PARAGRAPH) An additional usefulness of our proposed approach, which we do not verify in our research, is to give a new method to people become 
contributors to the Linux kernel. The process of starting to contribute to the Linux kernel can be unintuitive, which can cause 
people to distance themselves. Our approach provides to the community a new form of newcomers to start contributing by removing 
simple code duplications, while they learn the whole process of being a Linux contribuitor.

>>>>

This research is divided into two phases. On the \textbf{Phase I}, we will propose, build and validate a tool capable to indentify code 
duplications in function level for the C programming language, we expects this proposed tool to indentify code duplications
in the Linux kernel, as in our preliminary investigation the code files in the kernel is commonly a union of duplicated and 
nonduplicated functions. To validate the tool, we will do a triangulation of results by evaluate our tool in the code duplication
databases used in the formal literature and (DO NOT KNOW IF I REALLY WILL DO THIS) doing a empirical analyses in a set
of randomly selected codes of the AMD Display driver which our proposed tool claims that is a duplications. 
The detailed explication of how we will validate our tool is demonstrated in the Chapter \ref{cha:method}.

Given the first phase completion, we would have a validated tool to indentify code duplications in the Linux kernel 
context and we can move on to how mitigate these duplications, which comprehend the second phase of our research. On the 
\textbf{Phase 2}, we intend to discover ways to mitigate the code duplication detected in the linux kernel. 
To achieve our objective, we designed a etchnographic approach, which enables us to interact with the linux community
to collect artifacts validating or refuting our mitigation. The detailed explication of the etchnographic approach is demonstrated
in the Chatper \ref{cha:method}.

(POINTS TO CONSIDER: I do not like much this introduction, but is the best I could do)
(I DO NOT HAVE MORE A PLACE TO FIT THIS PARAGRAPH) An additional usefulness of our proposed approach, which we do not verify in our research, is to give a new method to people become 
contributors to the Linux kernel. The process of starting to contribute to the Linux kernel can be unintuitive, which can cause 
people to distance themselves. Our approach provides to the community a new form of newcomers to start contributing by removing 
simple code duplications, while they learn the whole process of being a Linux contribuitor.
